WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2019-02-24 review/referee_response_0.txt

iv) Figure 4: In the caption, could the authors explicitly indicate what the
plot shows in each of its panels (top and bottom)?

  > Response: Done.

v) Similar to i) How did you fit the mid-transit times and occultations shown
in Figure 4?

  > Response: We have added the following sentences in Section 3.2:
  > "We fit each model by assuming a Gaussian likelihood and sampling over the
  > posterior probability distributions. The prior for the quadratic model
  > allowed the period derivative to have any sign." We have clarified the
  > wording throughout from "decreasing-period model" to "quadratic model" to
  > reflect the latter point.

@@

  > Response: Corrected.

ii) In the caption of Figure 7: "with standard deviation (σpredicted)" -->
"with standard deviation (σpre-TESS)"

  > Response: Corrected.

********************************************************************************
Other changes:

* Added the following coauthors: Fei Dai, Natalia Guerrero, Bill Wohler,
  Douglas Caldwell.

### 2019-02-24 paper/ms.tex
address "major comment" #1 from referee

Table~2 gives the transit times we used in our analysis. We included
data from peer-reviewed literature for which the analysis was based on
observations of a single, complete transit, and for which the midpoint
was allowed to be a free parameter. We also required that the time
system be clearly documented. Many of the times were previously
compiled by \citet{hoyer_tramos_2013}. We confirmed that the times in
that paper were in agreement with the original sources and that
barycentric corrections had been performed when needed.

@@

In the \replaced{decreasing-period}{quadratic} model, the period derivative is
\begin{equation}
\dot{P}
  = - (4.00 \pm 0.38)\times 10^{-10}
  = - 12.6 \pm 1.2~{\rm ms}\,{\rm yr}^{-1}.
  \label{eq:dP_dt_obs}
\end{equation}
For comparison, the best-fitting period derivative of WASP-12b is
$\dot{P} = -29 \pm 3\,{\rm ms}\,{\rm yr}^{-1}$
\citep{maciejewski_departure_2016,patra_2017}.  If both planets are
truly falling onto their stars, then WASP-4b is falling at about half
the rate of WASP-12b.  In the precession model, the best-fit
eccentricity is
\begin{equation}
  e = (1.92^{+ 1.93}_{- 0.76})\times10^{-3}
\end{equation}
The longitude of periastron advances by $\dot{\omega} =
13.6^{+4.7}_{-3.6}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period is $27^{+10}_{-7}$ years.  All of the best-fitting parameters
(the medians of the posterior distributions) and the 68\% credible
intervals are reported in Table~4.

>>>>

Table~2 gives the transit times we used in our analysis. We included
data from peer-reviewed literature for which the analysis was based on
observations of a single\deleted{, complete} transit, and for which
the midpoint was allowed to be a free parameter. We also required that
the time system be clearly documented. Many of the times were
previously compiled by \citet{hoyer_tramos_2013}. We confirmed that
the times in that paper were in agreement with the original sources
and that barycentric corrections had been performed when needed.

@@

In the \replaced{decreasing-period}{quadratic} model, the period derivative is
\begin{equation}
\dot{P}
  = - (4.00 \pm 0.38)\times 10^{-10}
  = - 12.6 \pm 1.2~{\rm ms}\,{\rm yr}^{-1}.
  \label{eq:dP_dt_obs}
\end{equation}
For comparison, the best-fitting period derivative of WASP-12b is
$\dot{P} = -29 \pm 3\,{\rm ms}\,{\rm yr}^{-1}$
\citep{maciejewski_departure_2016,patra_2017}.  If both planets are
truly falling onto their stars, then WASP-4b is falling at about half
the rate of WASP-12b.  In the precession model, the best-fit
eccentricity is
\begin{equation}
  e = (1.92^{+ 1.93}_{- 0.76})\times10^{-3}
  \label{eq:e_obs}
\end{equation}
The longitude of periastron advances by $\dot{\omega} =
13.6^{+4.7}_{-3.6}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period is $27^{+10}_{-7}$ years.  All of the best-fitting parameters
(the medians of the posterior distributions) and the 68\% credible
intervals are reported in Table~4.

\added{
To assess the robustness of these results, we considered a few
possible systematic effects in the timing dataset.  One concern in the
pre-TESS timing measurements was incomplete phase coverage: a handful
of the transit times in Table~2 are from lightcurves with partial
gaps.  A separate issue is the effect of spot-crossing anomalies on
mid-transit time measurements.  Both effects lead to lightcurve
asymmetries which skew transit-time measurements.

We repeated the analysis desribed above, but omitted epochs -827,
-804, -537, and -208 because of gaps in their coverage.  We also
omitted epochs -526 and -561 because of visible spot anomalies during
the transits. (All epoch numbers are as in Table~2.)  The resulting
best-fit transit timing model parameters were all within $1\sigma$ of
the values quoted in Table~4.  The confidence intervals,
goodness-of-fit statistics $\chi^2$, and model comparison statistics
$(AIC, BIC)$ did not appreciably change.
}
